Northern Pikeminnow Abundance in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Chinook Salmon Populations

### 2022-01-29 analysis/paper/paper.Rmd
knit word doc

```{r adult-imp}
impact_df %>%
  select(season,
         perc_diet,
         juv_chnk,
         smolt_N,
         smolt_Lci,
         smolt_Uci,
         medsar,
         sdsar,
         adult_N,
         adult_Lci,
         adult_Uci) %>%
  mutate(juv_chnk = round(juv_chnk, 2),
         smolt_N = round(smolt_N, 0),
         smolt_Lci = round(smolt_Lci, 0),
         smolt_Uci = round(smolt_Uci, 0),
         medsar = round(medsar, 5),
         sdsar = round(sdsar, 5),
         adult_N = round(adult_N, 0),
         adult_Lci = round(adult_Lci, 0),
         adult_Uci = round(adult_Uci, 0)) %>%
  rename(Season = season,
         `p Fish` = perc_diet,
         `Fish Per NPM` = juv_chnk,
         `Fish N` = smolt_N,
         `Fish L CI` = smolt_Lci,
         `Fish U CI` = smolt_Uci,
         `Median SAR` = medsar,
         `SD SAR` = sdsar,
         `Adult N` = adult_N,
         `Adult L CI` = adult_Lci,
         `Adult U CI` = adult_Uci) %>%
  kable(booktabs = T,
        format.args = list(big.mark = ","),
        caption = "Estimates of the number of fish consumed for each season and diet scenario. The diet scenario indicates the proportion of the Northern Pikeminnow diet consisting of fish. The 'Fish Per NPM' column indicates the number of fish an individual Northern Pikeminnow to consume during the fall or spring seasons assuming an average weight of 10.3 (DSR) and 10.9 (NRR) grams for juvenile Chinook Salmon and is taken from each of the 18 bioenergetics model runs. The number of fish consumed (and 95% confidence intervals) are calculated using Northern Pikeminnow abundance estimates of 28,144 (95% CI: 14,378 - 59,978) for fall and 14,897 (95% CI: 7,610 - 31,747) for spring. The number of 'adult equivalents' is also estimated using a Lower Granite Dam smolt-to-adult rate (SAR) for Chinook Salmon from McCann et al. 2019.") %>%
  kable_styling(font_size = 8)

>>>>

```{r adult-imp, eval = F}
impact_df %>%
  select(season,
         perc_diet,
         juv_chnk,
         smolt_N,
         smolt_Lci,
         smolt_Uci,
         medsar,
         sdsar,
         adult_N,
         adult_Lci,
         adult_Uci) %>%
  mutate(juv_chnk = round(juv_chnk, 2),
         smolt_N = round(smolt_N, 0),
         smolt_Lci = round(smolt_Lci, 0),
         smolt_Uci = round(smolt_Uci, 0),
         medsar = round(medsar, 5),
         sdsar = round(sdsar, 5),
         adult_N = round(adult_N, 0),
         adult_Lci = round(adult_Lci, 0),
         adult_Uci = round(adult_Uci, 0)) %>%
  rename(Season = season,
         `p Fish` = perc_diet,
         `Fish Per NPM` = juv_chnk,
         `Fish N` = smolt_N,
         `Fish L CI` = smolt_Lci,
         `Fish U CI` = smolt_Uci,
         `Median SAR` = medsar,
         `SD SAR` = sdsar,
         `Adult N` = adult_N,
         `Adult L CI` = adult_Lci,
         `Adult U CI` = adult_Uci) %>%
  kable(booktabs = T,
        format.args = list(big.mark = ","),
        caption = "Estimates of the number of fish consumed for each season and diet scenario. The diet scenario indicates the proportion of the Northern Pikeminnow diet consisting of fish. The 'Fish Per NPM' column indicates the number of fish an individual Northern Pikeminnow to consume during the fall or spring seasons assuming an average weight of 10.3 (DSR) and 10.9 (NRR) grams for juvenile Chinook Salmon and is taken from each of the 18 bioenergetics model runs. The number of fish consumed (and 95% confidence intervals) are calculated using Northern Pikeminnow abundance estimates of 28,144 (95% CI: 14,378 - 59,978) for fall and 14,897 (95% CI: 7,610 - 31,747) for spring. The number of 'adult equivalents' is also estimated using a Lower Granite Dam smolt-to-adult rate (SAR) for Chinook Salmon from McCann et al. 2019.") %>%
  kable_styling(font_size = 8)
